Summary Tables

### 2020-05-18 summary_tables_outcomes.Rmd
Qualified scen names

---
title: "Summary Tables"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
    theme: united
---

@@

## Who hit whom matrix {#whw}

@@

      print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', var, ' matrix for ', city)))
      cat("\n")

>>>>

---
title: "Summary Tables"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: false
---

@@

## Who hit whom matrix of each case study (by baseline + scenarios) {#whw}

@@

      if (var == 'bl'){
        qualified_scen_name <- 'Baseline'
        scen <- ''
      }else if(var == "w_sc"){
        qualified_scen_name <- 'Walking'
      }else if(var == "bi_sc"){
        qualified_scen_name <- 'Bicycle'
      }else if(var == "car_sc"){
        qualified_scen_name <- 'Car'
      }else if(var == "mc_sc"){
        qualified_scen_name <- 'Motorcyle'
      }

      print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', qualified_scen_name, ' scenario matrix for ', city)))
      cat("\n")
